{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-17 paper/paper.tex
use package bussproofs
added multithreading typing rules
defined a typeable program

\usepackage{graphicx}
\usepackage{multicol}
\usepackage{amsbsy,amscd,amsfonts,amssymb,amstext,amsmath,latexsym,theorem}
\usepackage{todonotes}

@@

\begin{enumerate}
\item We have a partial ordered set $(LType, \leq)$ of local types
\item and typing judgments of the form $se, i \vdash_{seq} s \Rightarrow t$, where
$s, t \in LType$, $i \in \mathcal{P}$ and se is a securirty environment.
\end{enumerate}

@@

>>>>

\usepackage{graphicx}
\usepackage{multicol}
\usepackage{amsbsy,amscd,amsfonts,amssymb,amstext,amsmath,latexsym,theorem}
\usepackage{todonotes}
\usepackage{bussproofs}

@@

\todo{Explain intuition}
\begin{enumerate}
\item We have a partial ordered set $(LType, \leq)$ of local types, with an initial
      type $t_{init}$
\item and typing judgments of the form $se, i \vdash_{seq} s \Rightarrow t$, where
      $s, t \in LType$, $i \in \mathcal{P}$ and se is a securirty environment.
\end{enumerate}

@@

\todo{Place proofstrees into one line with minipages}
\begin{prooftree}
\AxiomC{P[i] $\in$ SeqIns}
\AxiomC{$se, i \vdash_{seq} s \Rightarrow t$}
\BinaryInfC{$se, i \vdash s \Rightarrow t$}
\end{prooftree}

\begin{prooftree}
\AxiomC{P[i] = \texttt{start} pc}
\AxiomC{$se(i) \leq se(pc)$}
\BinaryInfC{$se, i \vdash s \Rightarrow s$}
\end{prooftree}

The first rule states, that sequential commands are treated as usual
and the second rule ensures, that the security level of the entry point
of the spawned thread, is lower bounded by the level of the \texttt{start}
instruction.

A program is typeable in this type system $\mathcal{S}, se \vdash P$, where a function $\mathcal{S}:
\mathcal{P} \rightarrow LType$ that maps a local type to every program point
and a security environment $se$, iff $\mathcal{S}$ maps every initial program point
(including the ones of spawned threads) to $t_{init}$ and for every program point $j$ which is an
successor of $i$ there is a type $s \in LType$, such that $s$ is lower bounded
by $\mathcal{S}(j)$ and $se, i \vdash \mathcal{S}(i) \Rightarrow s$ holds.

\todo{Explain intuition}
